Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-12 paper.Rnw
reknit the paper after updating test data

% Citation information
\jnlcitation{
\cname{\author{Goode K.}, \author{H. Hofmann}, }
\cyear{2019},
\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
\cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
\cvol{volume, number and page}.}

@@

# Create the parallel coordinate plot (if needed)
if (!file.exists("figure-static/figure-10-1.png")) {

@@

  # Save the plot
  ggplot2::ggsave(
    plot = bullet_pcp,
    filename = "figure-10-1.png",
    width = 7.5,
    height = 3.5,
    units = "in",
    dpi = 1200
  )

  # Load the figure and then save as an EPS file
  bullet_pcp <- image_read("figure-static/figure-10-1.png")
  image_write(bullet_pcp, path = "figure-static/figure-10-1.eps", format = "eps")

@@

# Load and print the plot
knitr::include_graphics("figure-static/figure-10-1.eps")

@@

<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=

>>>>

% Citation information
\jnlcitation{
\cname{\author{Goode K.}, \author{H. Hofmann}, }
\cyear{2020},
\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
\cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
\cvol{volume, number and page}.}

@@

# File names for parallel coordinate plot
pcp_file_name_png = "figure-static/figure-10-1.png"
pcp_file_name_eps = "figure-static/figure-10-1.eps"

# Create the parallel coordinate plot (if needed)
if (!file.exists(pcp_file_name_png) | !file.exists(pcp_file_name_eps)) {

@@

  # Save the plot
  ggplot2::ggsave(
    plot = bullet_pcp,
    filename = pcp_file_name_png,
    width = 7.5,
    height = 3.5,
    units = "in",
    dpi = 1200
  )

  # Load the figure and then save as an EPS file
  bullet_pcp <- image_read(pcp_file_name_png)
  image_write(bullet_pcp, path = pcp_file_name_eps, format = "eps")

@@

# Load and print the plot
knitr::include_graphics(pcp_file_name_eps)

@@

<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
